\documentclass[Main]{subfiles}
\begin{document}


\textbf{BestFirst search strategy}

The BestFirst search strategy is implemented using a java.Util.PriorityQueue as the frontier. The queue utilizes the Comparator<Node> from Heuristics to sort the queue when adding elements. 
In order to optimize the state exploration, an extra frontier is used, oldFrontier. When a states is polled from the frontier, the rest of the states are moved to oldFrontier and frontier is cleared. The frontier is then used to store the unexplored states of the chosen node. In case of a dead end i.e. an empty frontier, an unexplored state is polled from oldFrontier. 
\\

\textbf{Heuristics function}

The heuristic functions functions calculates the Pythagorean distance from the agent to the box and from the box to the goal based on the array-coordinates of each. The goal and box coordinates are found in the pre-processing. 
As the implementation is right now, there can be and issue with multiples of same box and goal name, because it is stored in a hash map with the box and goal character as key.
\\

\textbf{Admissibility}

The heuristic function is admissible, as it calculates the Pythagorean distance between agent, box and goal, without regarding any possible obstacles. This will always be the shortest distance. 
\\

\textbf{Competition levels}

The SearchClient could not solve either of the competition levels. The reason for this being that the implemented algorithms doesn't take multiple and different goals and boxes into account.
\\

\textbf{Benchmark}

\begin{table}[h]
\begin{tabular}{llllll}
\rowcolor[HTML]{EFEFEF} 
\textbf{Level} & \textbf{Evaluation} & \textbf{Time} & \textbf{Memory used} & \textbf{Solution length} & \textbf{Nodes explored} \\
SAD1           & A*                  & 0.01 s        & 5.12 MB              & 19                       & 35                      \\
SAD1           & WA*                 & 0.01 s        & 5.12 MB              & 19                       & 19                      \\
SAD1           & Greed               & 0.01 s        & 5.12 MB              & 19                       & 19                      \\
SAD2           & A*                  & 0.01 s        & 5.12 MB              & 19                       & 19                      \\
SAD2           & WA*                 & 0.01 s        & 5.12 MB              & 19                       & 19                      \\
SAD2           & Greedy              & 0.01 s        & 5.12 MB              & 19                       & 19                      \\
custom         & A*                  & 0.01 s        & 5.12 MB              & 19                       & 19                      \\
custom         & WA*                 & 0.01 s        & 5.12 MB              & 19                       & 19                      \\
custom         & Greedy              & 0.01 s        & 5.12 MB              & 19                       & 19                      \\
FireFly        & A*                  & -           & -                  & -                      & -                     \\
FireFly        & WA*                 & -           & -                  & -                      & -                     \\
FireFly        & Greedy              & -           & -                  & -                      & -                     \\
Crunch         & A*                  & -           & -                  & -                      & -                     \\
Crunch         & WA*                 & -           & -                  & -                      & -                     \\
Crunch         & Greedy              & -           & -                  & -                      & -                     
\end{tabular}
\end{table}


\end{document}